Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
grammar, typo, compress a sentence
Left the verb in this time.

Our implementation guidelines emphasize on writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are thus directly written in pure Python. For
intensive numerical computations though, the library mostly relies on NumPy
vector operations, which allows for the code to remain concise, readable and
efficient. For all algorithms that cannot be easily and efficiently expressed as
NumPy operations, we rely on Cython \citep{behnel2011cython}  for writing the
critical parts and achieving decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms and decision trees.

@@

Another package that deserves mention is the Gensim topic modeling toolkit
\citep{rehurek2010gensim}.
Although its stated goal is not machine learning,
it does exemplify a style of API design for scalable processing of ``big data''
that takes a different approach than the comparable models in \sklearn.
Gensim's way of dealing with large datasets is to use algorithms
that have $O(1)$ space complexity and can be updated online,
called \textit{document streaming} by \citeauthor{rehurek2010gensim}.
The API is designed around the Python concept of an \textit{iterable}
(supported in the language by a restricted form of co-routines called
\textit{generators}).
While the text vectorization part of \sklearn
also uses irerables to some extent,
the emphasis is still largely on (mini-)batch processing,
even in the truly stateless, O(1) memory vectorizers
that implement the hashing trick of \citet{weinberger2009}.
This way of processing, as argued earlier in Section~\ref{sec:arrays},
reduces various forms of overhead
and allows users to make use of the abundance of memory in modern machines.
No attempt is made to hide this batch-oriented processing from the user,
allowing control over the amount of memory actually dedicated
to \sklearn algorithms.

>>>>

Our implementation guidelines emphasize writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are thus directly written in pure Python. For
intensive numerical computations though, the library mostly relies on NumPy
vector operations, which allows for the code to remain concise, readable and
efficient. For all algorithms that cannot be easily and efficiently expressed as
NumPy operations, we rely on Cython \citep{behnel2011cython}  for writing the
critical parts and achieving decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms and decision trees.

@@

Another package that deserves mention is the Gensim topic modeling toolkit
\citep{rehurek2010gensim}.
Although its stated goal is not machine learning,
it does exemplify a style of API design for scalable processing of ``big data''
that takes a different approach than the comparable models in \sklearn.
Gensim's way of dealing with large datasets is to use algorithms
that have $O(1)$ space complexity and can be updated online,
called \textit{document streaming} by \citeauthor{rehurek2010gensim}.
The API is designed around the Python concept of an \textit{iterable}
(supported in the language by a restricted form of co-routines called
\textit{generators}).
While the text vectorization part of \sklearn
also uses iterables to some extent,
the emphasis is still on (mini-)batch processing,
even in the truly stateless, O(1) memory vectorizers
that implement the hashing trick of \citet{weinberger2009}.
This way of processing, as argued earlier in Section~\ref{sec:arrays},
reduces various forms of overhead
and makes effective use of the abundance of memory in modern computers.
No attempt is made to hide this batch-oriented processing from the user,
allowing control over the amount of memory actually dedicated
to \sklearn algorithms.
